\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2014-02-02 motivation.tex
Paper updates

\begin{figure}[t!]
	\vspace{-10pt}
        \begin{SubFloat}{\label{delaycode:a}A human responsiveness
            system (HRTCS)}
        \begin{lstlisting}[style=sysj,morekeywords={sustain,send,receive,abort,await,emit,present,trap,pause,exit,wait_inbetween,wait_exact,suspend}]
{ // Clock-domain 1
while(true) {
  trap(T){
   // Abort if user touches the screen
   abort(TOUCH){
    {sustain GREEN_LIGHT;} //reaction R1
    || // synchronous parallel operator
    {
     //exit after any where from 50.3 to 200.3 ms.
     wait_inbetween (50.3 .. 200.3 ms); 
     exit(T); 
    } // reaction R2
   } do {send S(1);} // Send 1 if touched 
  } do {send S(0);} // Else Send 0
  pause; pause; pause; // pass some time before restarting
 }
}
>< // asynchronous operator
{ // Clock-domain 2
  while(true){ receive S; 
      if(#S == 1) counter++; else counter--;}
}
\end{lstlisting}
\end{SubFloat}
\begin{SubFloat}{\label{d:b}Timing diagram -- the X-axis shows the
    execution of the \texttt{wait\_inbetween} statement. The Y-axis is
    the time elapsed. The arrow shows one example of the expiration of
    the \mbox{\texttt{wait\_inbetween (50.3..200.3 ms)}} statement.}
  % \begin{figure}[h!]
    \centering
    \includegraphics[scale=0.7]{FF1}
  % \end{figure}
\end{SubFloat}
\caption{Programming a human responsiveness system (HRTCS) with
  \texttt{wait\_inbetween}}
% }
% \end{center}
\label{fig:1}
\end{figure}

The \texttt{wait\_inbetween (M..N)} statement postpones the program
control flow from moving to the proceeding statement for a minimum of
$M$ time units and a maximum of $N$ time units, as shown in
Figure~\ref{d:b}.

@@

The SystemJ pseudo-code~\cite{amal10} for such a system, along with the
expected timing behavior of the \texttt{wait\_inbetween} statement, is
shown in Figure~\ref{fig:1}. We use the SystemJ language in this paper,
because being a \textit{Globally Asynchronous Locally Synchronous}
(GALS) language it helps us easily describe a larger class of systems
(like HRTCS in Figure~\ref{fig:1}) compared to purely synchronous
languages like Esterel. Moreover, being a super-set of Esterel, SystemJ
allows us to explore the marriage of real-time and logical time not only
in the GALS, but also in the synchronous setting.

The SystemJ program is divided into two \hj{mutually asynchronous}
clock-domains, the first clock-domain continuously displays a green
light (\texttt{GREEN\_LIGHT} signal) on the touch screen sensor and
waits for the user to respond. If the user is able to touch the screen
within the specified time of at least 50.3 ms and at most 200.3 ms, a
positive response is sent to the second clock-domain. All the SystemJ
programming constructs used to implement this system are described in
Table~\ref{tab:1} \hj{and more details can be found
  in~\cite{amal10}}. The \texttt{wait\_inbetween} specification, which
models the non exact postponement between 50.3 ms and 200.3 ms is not
supported in the current language and cannot be compiled with the
current SystemJ compiler. We introduce such \texttt{wait\_inbetween}
statements in SystemJ. Such non exact real-time mechanisms are useful
for developing systems where the real-time postponement is not known or
should not be known a priori.

>>>>

\begin{figure}[t!]
	\vspace{-10pt}
        \begin{SubFloat}{\label{delay:a}A human responsiveness
            system (HRTCS)}
        \begin{lstlisting}[style=sysj,morekeywords={sustain,send,receive,abort,await,emit,present,trap,pause,exit,wait_inbetween,wait_exact,suspend}]
{ // Clock-domain 1
while(true) {
  trap(T){
   // Abort if user touches the screen
   abort(TOUCH){
    {sustain GREEN_LIGHT;} //reaction R1
    || // synchronous parallel operator
    {
     //exit after any where from 50.3 to 200.3 ms.
     wait_inbetween (50.3 .. 200.3 ms); 
     exit(T); 
    } // reaction R2
   } do {send S(1);} // Send 1 if touched 
  } do {send S(0);} // Else Send 0
  pause; pause; pause; // pass some time before restarting
 }
}
>< // asynchronous operator
{ // Clock-domain 2
  while(true){ receive S; 
      if(#S == 1) counter++; else counter--;}
}
\end{lstlisting}
\end{SubFloat}
\begin{SubFloat}{\label{d:b}Timing diagram -- the X-axis shows the
    execution of the \texttt{wait\_inbetween} statement. The Y-axis is
    the time elapsed. The arrow shows one example of the expiration of
    the \mbox{\texttt{wait\_inbetween (50.3..200.3 ms)}} statement.}
  % \begin{figure}[h!]
    \centering
    \includegraphics[scale=0.7]{FF1}
  % \end{figure}
\end{SubFloat}
\caption{Programming a human responsiveness system (HRTCS) with
  \texttt{wait\_inbetween}}
% }
% \end{center}
\label{fig:1}
\end{figure}

The \texttt{wait\_inbetween (M..N)} statement postpones the program
control flow from proceeding to the following statement for a minimum of
$M$ time units and a maximum of $N$ time units, as shown in
Figure~\ref{d:b}.

@@

The SystemJ pseudo-code~\cite{amal10} for such a system, along with the
expected timing behavior of the \texttt{wait\_inbetween} statement, is
shown in Figure~\ref{fig:1}. We use the SystemJ language in this paper,
because being a \textit{Globally Asynchronous Locally Synchronous}
(GALS) language it helps us easily describe a larger class of systems
(like HRTCS in Figure~\ref{delay:a}) compared to purely synchronous
languages like Esterel. Moreover, being a super-set of Esterel, SystemJ
allows us to explore the marriage of real-time and logical time not only
in the GALS, but also in the synchronous setting.

The SystemJ program in Figure~\ref{delay:a} is divided into two
\hj{mutually asynchronous} clock-domains, the first clock-domain
continuously displays a green light (\texttt{GREEN\_LIGHT} signal) on
the touch screen sensor and waits for the user to respond. If the user
is able to touch the screen within the specified time of at least 50.3
ms and at most 200.3 ms, a positive response is sent to the second
clock-domain. All the SystemJ programming constructs used to implement
this system are described in Table~\ref{tab:1} \hj{and more details can
  be found in~\cite{amal10}}. The \texttt{wait\_inbetween}
specification, which models the non exact postponement between 50.3 ms
and 200.3 ms is not supported in the current language and cannot be
compiled with the current SystemJ compiler. We introduce such
\texttt{wait\_inbetween} statements in SystemJ. Such non exact real-time
mechanisms are useful for developing systems where the real-time
postponement is not known or should not be known a priori.
